### 2021-02-28 CV/cv-sections/papers.tex
-

\cventry
{Grigory Malinovsky, Dmitry Kovalev, Elnur Gasanov, Laurent Condat, Peter Richtárik} % Authors
{From Local SGD to Local Fixed Point Methods for Federated Learning} % Title
{\href{https://proceedings.icml.cc/paper/2020/hash/53fdae58e861476b182b0cd6beade809-Abstract.html}{ICML 2020}} 
{03 Apr 2020} % Date
{}

\cventry
{Zhize Li, Dmitry Kovalev, Xun Qian, Peter Richtárik} % Authors
{Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} % Title
{\href{https://proceedings.icml.cc/paper/2020/hash/18ad9899f3f21a5a1583584d5f11c0c0-Abstract.html}{ICML 2020}} 
{26 Feb 2020} % Date
{}

@@

\cventry
{Filip Hanzely, Dmitry Kovalev, Peter Richtárik} % Authors
{Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} % Title
{\href{https://proceedings.icml.cc/paper/2020/hash/b571ecea16a9824023ee1af16897a582-Abstract.html}{ICML 2020}} 
{11 Feb 2020} % Date
{}

>>>>

\cventry
{Grigory Malinovsky, Dmitry Kovalev, Elnur Gasanov, Laurent Condat, Peter Richtárik} % Authors
{From Local SGD to Local Fixed Point Methods for Federated Learning} % Title
{\href{http://proceedings.mlr.press/v119/malinovskiy20a.html}{ICML 2020}} 
{03 Apr 2020} % Date
{}

\cventry
{Zhize Li, Dmitry Kovalev, Xun Qian, Peter Richtárik} % Authors
{Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} % Title
{\href{http://proceedings.mlr.press/v119/li20g.html}{ICML 2020}} 
{26 Feb 2020} % Date
{}

@@

\cventry
{Filip Hanzely, Dmitry Kovalev, Peter Richtárik} % Authors
{Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} % Title
{\href{http://proceedings.mlr.press/v119/hanzely20b.html}{ICML 2020}} 
{11 Feb 2020} % Date
{}
